PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
minor edits
Adapted the code for retro and baseline OCI-R scores.

Calculate sum score for OCI-R retro
```{r coping ocir sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1)

@@

# Calulate total score
ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 3)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores

@@

Calculate sum score for OCI-R base
```{r coping ocir sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
ocir.items_base = c(
  "ocir.little_interest_or_pleasure_in_doing_things_base_numeric",
"ocir.feeling_down_depressed_or_hopeless_base_numeric",
"ocir.staying_asleep_sleeping_trouble_base_numeric",
"ocir.feeling_tired_or_having_little_energy_base_numeric",
"ocir.poor_appetite_or_overeating_base_numeric",
"ocir.feeling_bad_failure_family_base_numeric",
"ocir.trouble_concentrating_reading_newspaper_base_numeric",
"ocir.moving_fidgety_noticed_opposite_base_numeric",
"ocir.dead_hurting_thoughts_base_numeric"
)

# Calulate total score
ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
                                    items = coping.glad.ocir.raw.id[ocir.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 3)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores

>>>>

Calculate sum score for OCI-R retro
```{r coping ocir sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

@@

# Calulate total score
ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores

@@

Calculate sum score for OCI-R base
```{r coping ocir sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
ocir.items_base = c(
  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
  "ocir.arranged_things_change_upset_base",
  "ocir.repeat_feel_numbers_base",
  "ocir.clean_simply_wash_feel_base",
  "ocir.mind_upset_unpleasant_thoughts_base",
  "ocir.afraid_avoid_throwing_things_base",
  "ocir.light_switches_water_taps_base",
  "ocir.arranged_things_base",
  "ocir.good_feel_bad_numbers_base",
  "ocir.hands_longer_wash_base",
  "ocir.saved_things_base",
  "ocir.frequently_difficulty_rid_nasty_base",
  "ocir.i_check_things_more_often_than_necessary_base",
  "ocir.arranged_properly_objects_upset_base",
  "ocir.feel_compelled_count_things_base",
  "ocir.strangers_touch_touched_difficult_base",
  "ocir.control_difficult_find_thoughts_base",
  "ocir.i_collect_things_i_dont_need_base"
)

# Calulate total score
ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
                                    items = coping.glad.ocir.raw.id[ocir.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores
